---
title: "Examples from package `kohonen.hexagons`"
author: "Vilmantas Gegzna"
date: "`r Sys.Date()`"
output:
    rmarkdown::html_vignette: 
        toc: yes
        number_sections: yes
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r Load packages, message=FALSE,warning=FALSE}
library(kohonen.hexagons)
library(kohonen)
library(pander)
```
```{r options1, echo = FALSE, message = FALSE, warning = FALSE}
optDEF <- knitr::opts_chunk$get()
knitr::opts_chunk$set(comment = "#>",
                      fig.align = 'center')
op <- par(mar=c(1,1,1,1))
```



Functions
=========


Functions `hexagonMap` and `hexagonPT`
--------------------------------------


Plot single hexagon.

```{r}
plot.new()
hexagonPT(.5,.5, r = .3)
```

Plot a map of hexagons.

```{r}
 data <- class::somgrid(8,6,"hexagonal")$pts
 head(data)
 x <- data[,"x"]
 y <- data[,"y"]

 hexagonMap(x, y)

# Add color
 hexagonMap(x, y, col = "yellow")

# Add colors and text
 hexagonMap(x, y,
      col = c("tomato1","skyblue","orange"),
      border = c("red", "black"))

 text(x,y,1:length(x), cex = .6)
 title("Hexagonal cells \n with cell ID number")

```

Function `hexagonPT_verticles`
--------------------------------

```{r hexagonPT_verticles,  fig.show='hold'}
hexagonPT_verticles(1,1)
```

### Names and positions of polygon verticles

A (top)  
B (left upper)  
C (left lower)  
D (bottom)  
E (right)  
F (right upper).

```{r hexagonPT_verticles 2, echo = FALSE}
verticles <- hexagonPT_verticles(1,1)  %>% t

plot(verticles, type = "n", main = "Names of polygon verticles")  # initialize a plot
polygon(verticles, border = "grey")
text(verticles,labels = LETTERS[1:6], col = "blue")

```

Function `hex_neighbourhood_line_pos`
----------------------------------
```{r hex_neighbourhood_line_pos}
hex_neighbourhood_line_pos(x, y)  %>% head
```



Function `hex_neighbour_dist`
----------------------------------

```{r}
library(kohonen)
data("Spectra2", package = "spHelper")

som_model <- som(Spectra2$spc, grid = somgrid(7,7,"hexagonal"))
hex_neighbour_dist(som_model)  %>% head
```

Function `hexagon_default_params`
----------------------------------

```{r hexagon_default_params}
hexagon_default_params()      %>% pander

hexagon_default_params(r = 1) %>% pander

hexagon_default_params(l = 1) %>% pander

data <- class::somgrid(8,6,"hexagonal")$pts
hexagon_default_params(x = data[,"x"], y = data[,"y"]) %>% pander

hexagon_default_params(x = data[,"x"], y = data[,"y"]*2) %>% pander

hexagon_default_params(x = data[,"x"]*2, y = data[,"y"]) %>% pander
```



Default info (DO NOT READ)
============================

<font size=5 color="red"> Do not read further. Vignette is not completed yet. </font>



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
